Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-21 datapaper_conclusion.tex
Chen edit

\section{Conclusions}

@@

>>>>

\section{Conclusion and Discussion}

@@

It might be noticed that all plants (respectively for Arabidopsis and bean) in MSU-PID belong to the same genotype and no treatments applied. %This would entail that the proposed dataset cannot be used to investigate computer vision algorithms or imaging modalities in relation to group differences. Could the authors comment on this? This is true. We are not comparing group differences, based on morphology (for example).
This is because we think a fundamental issue with visual phenotyping, i.e. accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences. The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.  %I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences.

### 2015-07-21 datapaper_hardware.tex
fig2
fig 2
Chen edit

\begin{figure}
  \includegraphics[width=\linewidth,trim=55 100 200 70,clip]{Figures/hardware}
\caption{The hardware setup for our data collection.}
\label{fig:hardware}
\end{figure}

@@

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
%
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

@@

\subsubsection{Image collection} 
The imagery data, including the fluorescent image, the IR reflectance image,  the color image, and the $3$D depth image, were collected once every hour. First, the fluorescent image and the IR reflectance image were captured sequentially using the same camera without any delay.
% 
After five minutes, the $3$D depth image and the color image were captured using the Creative Senz3D sensor. The captured depth points were then transformed into the world coordinates and expressed in the unit of $mm$. Since plant leaves do not move quickly, the five minutes gap between the camera operations do not cause severe problems in image calibration.

>>>>

\begin{figure}
  \includegraphics[width=0.95\linewidth]{Figures/hardware}
\caption{The hardware setup for our data collection.}
\label{fig:hardware}
\end{figure}

@@

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
Since $940nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800nm$) in the region where we do IR reflectance ($940nm$)~\cite{butler1964actton}.
%
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

@@

\subsubsection{Image collection}
The imagery data, including the fluorescent image, the IR reflectance image,  the color image, and the $3$D depth image, were collected once every hour.
%
Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and the IR reflectance images collected sequentially at 2 minute intervals by the IR filtered CCD camera.
%
No substantial movements or growth were observed within the about four minute period required for image capture using all four modalities, minimizing potential problems in image calibration.

%First, the fluorescent image and the IR reflectance image were captured sequentially using the same camera without any delay.
%
%After five minutes, the $3$D depth image and the color image were captured using the Creative Senz3D sensor. 
%Since plant leaves do not move quickly, the five minutes gap between the camera operations do not cause severe problems in image calibration.

### 2015-07-21 datapaper_intro.tex
Chen edit

@@

The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments.
As a result, MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
Finally, to provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.

>>>>

One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield and resilience to environmental stress.  For the approach to be of practical use, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
%
The capacity to identify and track individual leaves throughout experiments will be important for more clearly defining phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress. For example, decreases in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}. In this case, mapping distributions to individual leaves can be used to distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
%
In addition, using more detailed information, such as leaf angle and height/position as well as canopy density/size, it should be possible to improve estimates of total photosynthetic capacity over time (particularly for plants with more complex canopies, like common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.

@@

%
The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments.
As a result, MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
Finally, to provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.

### 2015-07-21 datapaper_prior.tex
final edits
Chen edit

We summarize some existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}.
In terms of potential applications of these databases, they can be categorized into two types.
The first type is for the general purpose of recognizing a particular species of tree or plant.
The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners.
The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is utilized to train a leaf classifier.
The most recent leafsnap project~\cite{kumar2012leafsnap} is an impressive effort that includes a very large dataset of leaves for $184$ tree types.
A mobile phone application is also developed to make the leaf classification system portable.
Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs.~weed.
Note that except for~\cite{haug2014crop} where images are captured in the wild for a large area of plant, other databases in this type normally capture only a {\it single} leaf is in a relatively constrained imaging environment.
Therefore, the challenging problem of leaf segmentation has been bypassed.
% Note that in this type of databases, normally only a {\it single} leaf is imaged in a relatively constrained imaging environment and as a result, the challenging problem of leaf segmentation has been bypassed.

@@

The four sensing modalities provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes. Chlorophyll fluorescence measurement is an effective method to detect photosynthesis. For example, steady-state chlorophyll fluorescence is a relative measure of photosynthetic health in drought stress~\cite{chen2014dissecting}. The quantum efficiency of photosystem II can be approximated by comparing chlorophyll fluorescence levels under two light conditions~\cite{baker2008chlorophyll}. The dense depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}. By including dense depth for a plant database we anticipate enabling development of new 3D plant canopy analysis algorithms, thus probing the total energy intake and storage. The infrared measurement enables researchers to detect chloroplast movements, which have been proposed to optimize light capture and minimize photodamage to the photosynthetic apparatus~\cite{Dutta2015Non}.

>>>>

We summarize existing publicly available databases that are most related to our work in Table~\ref{tab:database}.
In terms of potential applications of these databases, they can be categorized into two types.
The first type is for the general purpose of recognizing a particular species of tree or plant.
The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners.
The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is utilized to train a leaf classifier.
The most recent leafsnap project~\cite{kumar2012leafsnap} is an impressive effort that includes a very large dataset of leaves for $184$ tree types.
A mobile phone application is also developed to make the leaf classification system portable.
Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs.~weed.
Note that except for~\cite{haug2014crop} where images are captured in the wild for a large area of plant, other databases in this type normally capture only a {\it single} leaf is in a relatively constrained imaging environment.
Therefore, the challenging problem of leaf segmentation has been bypassed.
% Note that in this type of databases, normally only a {\it single} leaf is imaged in a relatively constrained imaging environment and as a result, the challenging problem of leaf segmentation has been bypassed.

@@

%One of our data modalities is dense depth measurement. This has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}. By including dense depth for a plant database we anticipate enabling development of new 3D plant shape analysis algorithms.

The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes. The use of chlorophyll fluorescence at $730$ to $750nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
The dense depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}. By including dense depth for a plant database we anticipate enabling development of new 3D plant canopy analysis algorithms, thus probing the total energy intake and storage.
Near infrared (IR) reflectance has been used by others to detect water content in leaves~\cite{chen2014dissecting}.  However, it may also be useful in determining leaf angle and curvature.  Furthermore, since imaging occurs at a wavelength that is effectively non-absorbing for photosynthesis or known light receptors~\cite{butler1964actton,eskins1992light} in plants, it can be used for imaging during the night cycle to observe night time leaf expansion or in some cases circadian movements~\cite{mcclung2006plant}.

### 2015-07-21 datapapr_labeling.tex
Chen edit

>>>>

It is often argued which is the best setting due to the trade-off between the image resolution and the throughput of phenotyping experiments. 
We chose to image a whole tray of Arabidopsis at lower resolution rather than an individual at higher resolution, because it better reflects high-throughput protocols, which in practice allows direct comparison of multiple genotypes in the same experiment.  
In contrary, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bush plants.
